---
title: "p8105_hw5_mc5503.Rmd"
author: "mc5503"
date: '2023-11-07'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
```
# Problem 1

## data operations
```{r}
data1=read_csv("data/homicide-data.csv")|>janitor::clean_names()
str(data1)

time_range=range(data1|>pull(reported_date))
```
There are 52179 observations from `r as.Date(as.character(time_range[1]),format = "%Y%m%d")` to `r as.Date(as.character(time_range[2]),format = "%Y%m%d")`. There are `r ncol(data1)` variables, containing the time, location of each homicide and demographic characteristics of victim. There are total `r length(unique(data1|>pull(city)))` cities included in the data.

## calculate for Baltimore
```{r}
data1=data1|>mutate(city_state=paste(city,state,sep = ","))

n_obs=nrow(data1|>filter(city=='Baltimore'))

n_arrest=nrow(data1|>filter(city=='Baltimore'& disposition!="Closed by arrest"))

result=prop.test(x=n_arrest,n=n_obs)

p_est=broom::tidy(result)|>pull(estimate)

conf_low=broom::tidy(result)|>pull(conf.low)

conf_high=broom::tidy(result)|>pull(conf.high)

p_est

conf_low

conf_high
```

The proportion of unsolved (unarrested) homicide in Baltimore is `r p_est`, and the CI is [`r c(conf_low,conf_high)`].

## calculate for all cities
```{r}
prop_f=function(city_name)
{
  n_obs=nrow(data1|>filter(city==city_name))

  n_arrest=nrow(data1|>filter(city==city_name & disposition!="Closed by arrest"))

  result=prop.test(x=n_arrest,n=n_obs)

  p_est=broom::tidy(result)|>pull(estimate)

  conf_low=broom::tidy(result)|>pull(conf.low)

  conf_high=broom::tidy(result)|>pull(conf.high)
  
  tibble(p_est,conf_low,conf_high)
}

#prop_f("Baltimore")

city_list=unique(data1|>pull(city))

output = vector("list", length = length(city_list))

output=map(city_list,prop_f)

#data_nest=nest(data1, data = c(-city))

prop_results=tibble(city_list,output)|>unnest(cols = output)
```

## plots
```{r}
prop_results|>
  mutate(city_list=forcats::fct_reorder(city_list,p_est))|>
  ggplot(aes(x=city_list,y=p_est,ymin=conf_low,ymax=conf_high,color=city_list))+
  geom_point()+
  geom_errorbar()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))+
  theme(legend.position="none")
```

